\documentclass[12pt, titlepage]{article}

\usepackage{booktabs}
\usepackage{tabularx}
\usepackage{hyperref}
\usepackage{longtable}
\usepackage{amsmath}
\usepackage{siunitx}

\hypersetup{
    colorlinks,
    citecolor=blue,
    filecolor=black,
    linkcolor=red,
    urlcolor=blue
}
\usepackage[round]{natbib}

\input{../Comments.text}
\input{../Common.text}

% Used so that cross-references have a meaningful prefix
\newcounter{fitnum} %Flocking Input Test Number
\newcommand{\dthefitnum}{ITF\thefitnum}
\newcommand{\ftref}[1]{ITF\ref{#1}}
\newcounter{oitnum} %Obstacles Input Test Number
\newcommand{\dtheoitnum}{OTF\theoitnum}
\newcommand{\otref}[1]{OTF\ref{#1}}
\newcounter{mitnum} %Integration Method Test Number
\newcommand{\dthemitnum}{MTF\themitnum}
\newcommand{\mtref}[1]{MTF\ref{#1}}

\begin{document}

\title{System Verification and Validation Plan for \progname{}} 
\author{\authname}
\date{\today}
	
\maketitle

\pagenumbering{roman}

\section*{Revision History}

\begin{tabularx}{\textwidth}{p{3cm}p{2cm}X}
\toprule {\bf Date} & {\bf Version} & {\bf Notes}\\
\midrule
2026/02/13 & 1.0 & Initial VnV plan.\\
2026/04/07 & 1.1 & Modified based on the reviewer's feedback\\
2026/04/17 & 1.2 & Added Test about Realism \\
2026/04/18 & 1.3 & Finish the Unit Test Section \\
\bottomrule
\end{tabularx}


\newpage

\tableofcontents

\listoftables

\newpage

\section{Symbols, Abbreviations, and Acronyms}

For complete symbols used within this software, please refer 
the \citet{SRS} Section 1.

\subsection{Table of Symbols}

\renewcommand{\arraystretch}{1.2}
%\noindent \begin{tabularx}{1.0\textwidth}{l l X}
\noindent \begin{longtable}{l l p{12cm}} \toprule
\textbf{symbol} & \textbf{unit} & \textbf{description}\\
\midrule 
$\mathbf{A}_\mathbf{t}$ & -- & The alignment metric of flocking at time t \\
$\mathbf{C}_\mathbf{t}$ & \si{\metre} & The flocking cohesion at time t\\
$k$  & -- & Index of one of the obstacle in the obstacle set \\
$k_a$  & \si{\kilogram\per\second} & The weighting coefficient of alignment forces \\
$k_c$  & \si{\kilogram\per\second\squared} & The weighting coefficient of cohesion forces \\
$k_g$  & \si{\kilogram\per\second\squared} & The weighting coefficient of goal seeking forces \\
$k_o$  & \si{\kilogram\metre\squared\per\second\squared} & The weighting coefficient of obstacle avoidance forces \\
$k_s$  & \si{\kilogram\metre\squared\per\second\squared} & The weighting coefficient of separation forces \\
$N$ & -- & The total number of agent in the flocking model \\
$\mathbf{M}$ & - & The selected numerical integration method \\
$\mathbf{p}_{k}$ & \si{\metre} & The position of obstacle \textit{k} \\
$\mathbf{p}_\mathbf{t}$ & \si{\metre} & The position of flocking center at time t \\
$\mathbf{r}_{k}$ & \si{\metre} & The radius of obstacle \textit{k} \\
$\Delta t$ & \si{\second} & The time step used by the numerical integration method \\
$\mathbf{v}_{i,t}$ & \si{\metre\per\second} & The velocity of agent \textit{i} at time t\\
$\bar{v}_\mathbf{t}$ & \si{\metre\per\second} & The mean speed of flocking at time t\\
\bottomrule
\end{longtable}

\subsection{Abbreviations, and Acronyms}

\renewcommand{\arraystretch}{1.2}
\begin{tabular}{l l} 
  \toprule		
  \textbf{symbol} & \textbf{description}\\
  \midrule 
  R & Requirement \\
  NFR & Nonfunctional Requirement \\
  SRS & Software Requirements Specification\\
  VnV & Verification and Validation \\
  MG & Module Guide \\
  MIS & Module Interface Specification \\
  CI & Continuous integration \\
  EEuler & Explicit Euler\\
  RK4 & Runge-Kutta 4\\
  SIEuler & Semi-Implicit Euler\\
  \bottomrule
\end{tabular}\\

\newpage

\pagenumbering{arabic}

\section{General Information}

This document provide an introductory blurb and roadmap of the Verification and 
Validation plan for the project Numerical Integration of Flocking Dynamics over 
Structured Terrains (\progname{}), with the goal of ensuring that the 
requirements specified in the SRS are satisfied.

The document includes general information and planning details, specific test 
cases for both functional and nonfunctional requirements, as well as details of 
unit testing.

\subsection{Summary}

The software being testing is a program designed to perform group animation 
simulations. It employs multiple numerical integration methods to simulate the 
movement of a group of agents navigating toward a target point within an 
environment containing obstacles. The purpose of the software is to compare the 
resulting group states and the realism of the generated group animations 
produced by different numerical integration methods.

\subsection{Objectives}

The most important objective of this document is to build confidence in the 
correctness of the software \progname{}. This objective is achieved by 
designing tests corresponding to the functional requirements specified in the 
SRS. In addition, validation activities are conducted to assess nonfunctional 
requirements, including usability, maintainability and the realism of the 
simulation results.

\subsection{Extras}

The extras of this project include the following documents:

\begin{itemize}
\item User Manual \\
The User Manual provides detailed instructions on how to install, configure, 
and operate the software, which is intended to support users in effectively 
utilizing the simulation program.

\item Performance Report \\
The Performance Report presents an evaluation of the computational performance 
of the software. It includes analysis of execution time, resource usage, 
and efficiency across different numerical integration methods.
\end{itemize}

\subsection{Relevant Documentation}

The related documents include the Problem Statement (\citet{ProblemStatement}), 
which describes the proposed idea of the project, the Software Requirements 
Specification (\citet{SRS}), which specifies the software requirements in 
detail, and \citet{MIS}.

\section{Plan}

This section presents the test plan for the software. It includes the 
Verification and Validation team (\ref{vnv_team}), the SRS verification 
plan (\ref{srs_verif}), the design verification plan (\ref{design_verif}), 
the implementation verification plan (\ref{vnv_verif}), the automated testing 
and verification tools (\ref{auto_tool}), and the overall software validation 
plan (\ref{soft_valid}) .

\subsection{Verification and Validation Team} \label{vnv_team}

\begin{itemize}
\item Yibing Mei - Developer \\
Create and manage all project documents, implement the software, and test with 
the VnV plan to ensure the quality of the software.

\item Dr.\ Spencer Smith - Supervisor \\
Review all documents.

\item Mohsen Bakhtiari - Domain Expert \\
Review all documents.
\end{itemize}

\subsection{SRS Verification} \label{srs_verif}

The SRS Verification is done through a structured review process. First, 
Supervisor (Dr.\ Spencer Smith) and Domain Expert (Mohsen Bakhtiari) will review 
using the \citet{SRSChecklist}, which is designed by Dr.\ Spencer Smith. Feedback 
should be create as GitHub issues. The developer (Yibing Mei) is responsible to 
address issues to ensure the quality of SRS document.

\subsection{Design Verification} \label{design_verif}

The design will be verified by Supervisor (Dr.\ Spencer Smith) and Domain 
Expert (Mohsen Bakhtiari). Feedback will be provided through the creation of 
issues on GitHub. The developer (Yibing Mei) will review, address, and resolve 
these issues.

\subsection{Verification and Validation Plan Verification} \label{vnv_verif}

The VnV plan will be reviewed by Supervisor (Dr.\ Spencer Smith) and Domain 
Expert (Mohsen Bakhtiari) following the \citet{VnVChecklist}. Feedback will be 
communicated through the creation of GitHub issues. The developer (Yibing Mei) 
will address the reported issues and update the document accordingly.

\subsection{Implementation Verification}

Implementation verification will be achieved through the execution of the 
test cases specified in Section~\ref{sec_systest}. Detailed descriptions of 
the unit testing approach are provided in Section~\ref{sec_unittest}. 
Furthermore, the final class presentation will be used as a code walkthrough.

\subsection{Automated Testing and Verification Tools} \label{auto_tool}

This project is planned to be developed in Unity using C\#, and some of Unity's 
built-in tools and package will be used for automated testing.

\begin{itemize}
\item Linters: Roslyn Analyzers(StyleCop.Analyzers).

\item System and Unit Tests: Unity Test Framework.

\item ode Coverage: Unity Code Coverage Package.

\item Continuous Integration (CI) : GitHub Actions to run automated tests upon 
pull request to main branch.
\end{itemize}

\subsection{Software Validation} \label{soft_valid}

Software validation is beyond the scope of this project.

The foundation of the project is primarily theoretical, and the outputs are 
intended to illustrate general trends rather than produce meaningful numerical 
results. Consequently, even if external data were available, direct comparison 
for validation purposes would not be appropriate.

The validation process would require evaluation by domain experts to confirm 
the correctness of models and equations, and ensure that the theoretical 
formulations have been implemented accurately. This level of assessment is 
outside the responsibility and scope of the current project.

\section{System Tests} \label{sec_systest}

This section presents the detailed test cases for both the functional 
requirements (\ref{test_func}) and the nonfunctional requirements (\ref{test_nonfunc}).

\subsection{Tests for Functional Requirements} \label{test_func}

These test cases are designed to verify the functional requirements specified 
in the \citet{SRS} (Section 5.1). The traceability between the requirements and 
the corresponding test cases is illustrated in Table~\ref{tblTrace}.

\subsubsection{Input Test} \label{inputTest}

This section covers the test cases for R1 and R2 specified in the \citet{SRS}, 
including verification of input validity and confirmation that appropriate 
error messages are returned when inputs are invalid. Due to the large number 
of input parameters, they are organized into three groups based on the aspects 
of the system behavior they control.

In general, invalid inputs are unlikely due to the presence of a graphical 
input interface. However, input validation must still be performed at the 
backend to ensure robustness and correctness.
		
\paragraph{Input Tests for Flocking Parameters}

\begin{enumerate}

\item{test-input-Flocking\\}

Control: Automatic
					
Initial State: The numerical integration method is SIEuler, with no obstacles 
present.
					
Input: The Input column in Table~\ref{TblITFlocking}
					
Output: The Output column in Table~\ref{TblITFlocking}

Test Case Derivation: The constraints on the flocking parameters ensure that 
the flocking behavior can remain in a fundamentally stable state. The software 
will return an error message for any invalid inputs or pass valid inputs on to 
the next step.
					
How test will be performed: The developer will create the test cases and run 
them automatically using the Unity Test Framework.
\end{enumerate}

\begin{longtable}{c|c c c c c c c|c c}
\caption{Input and Output - Flocking} \label{TblITFlocking} \\
\hline
\multicolumn{1}{c|}{Index} & \multicolumn{7}{c|}{Input} & \multicolumn{2}{c}{Output} \\
\hline
& $N$ & ${\Delta t}\text{(s)}$ & $k_a$ & $k_c$ & $k_s$ & $k_o$ & $k_g$ & Valid? & Error Message \\
\hline
ITF\refstepcounter{fitnum}\thefitnum & 100 & 0.01 & 0.5 & 0.5 & 0.5 & 0.5 & 0.5 & Y & No error message. \\
\hline
ITF\refstepcounter{fitnum}\thefitnum & -10 & 0.01 & 0.5 & 0.5 & 0.5 & 0.5 & 0.5 & N & $N$ must be in [1, 5000]. \\
\hline
ITF\refstepcounter{fitnum}\thefitnum & 100 & -0.01 & 0.5 & 0.5 & 0.5 & 0.5 & 0.5 & N & ${\Delta t}$ must be in [0.005, 0.1]. \\
\hline
ITF\refstepcounter{fitnum}\thefitnum & 100 & 0.01 & 3.5 & 0.5 & 0.5 & 0.5 & 0.5 & N & $k_a$ must be in [0, 2.0]. \\
\hline
ITF\refstepcounter{fitnum}\thefitnum & 100 & 0.01 & 0.5 & 3.5 & 0.5 & 0.5 & 0.5 & N & $k_c$ must be in [0, 2.0]. \\
\hline
ITF\refstepcounter{fitnum}\thefitnum & 100 & 0.01 & 0.5 & 0.5 & 3.5 & 0.5 & 0.5 & N & $k_s$ must be in [0, 2.0]. \\
\hline
ITF\refstepcounter{fitnum}\thefitnum & 100 & 0.01 & 0.5 & 0.5 & 0.5 & 3.5 & 0.5 & N & $k_o$ must be in [0, 2.0]. \\
\hline
ITF\refstepcounter{fitnum}\thefitnum & 100 & 0.01 & 0.5 & 0.5 & 0.5 & 0.5 & 3.5 & N & $k_g$ must be in [0, 2.0]. \\
\hline
ITF\refstepcounter{fitnum}\thefitnum &   & 0.01 & 0.5 & 0.5 & 0.5 & 0.5 & 0.5 & N & Data missing for $N$. \\
\hline
ITF\refstepcounter{fitnum}\thefitnum & 100 &   & 0.5 & 0.5 & 0.5 & 0.5 & 0.5 & N & Data missing for ${\Delta t}$. \\
\hline
ITF\refstepcounter{fitnum}\thefitnum & 100 & 0.01 &   & 0.5 & 0.5 & 0.5 & 0.5 & N & Data missing for $k_a$. \\
\hline
ITF\refstepcounter{fitnum}\thefitnum & 100 & 0.01 & 0.5 &   & 0.5 & 0.5 & 0.5 & N & Data missing for $k_c$. \\
\hline
ITF\refstepcounter{fitnum}\thefitnum & 100 & 0.01 & 0.5 & 0.5 &   & 0.5 & 0.5 & N & Data missing for $k_s$. \\
\hline
ITF\refstepcounter{fitnum}\thefitnum & 100 & 0.01 & 0.5 & 0.5 & 0.5 &   & 0.5 & N & Data missing for $k_o$. \\
\hline
ITF\refstepcounter{fitnum}\thefitnum & 100 & 0.01 & 0.5 & 0.5 & 0.5 & 0.5 &   & N & Data missing for $k_g$. \\
\hline
\end{longtable} 

\paragraph{Input Tests for Obstacle Parameters}

\begin{enumerate}
\item{test-input-obstacle\\}

Control: Automatic
					
Initial State: The numerical integration method is SIEuler, and the flocking 
parameters is in Table~\ref{TblFlockParameters}.
					
Input: The Input column in Table~\ref{TblITObstacles}
					
Output: The Output column in Table~\ref{TblITObstacles}

Test Case Derivation: The constraints on the obstacle parameters ensure that 
the obstacles are meaningful and may influence the flocking behavior. Obstacles 
are optional; however, if present, each obstacle $k$ must have both $\mathbf{p}_k$ 
and $\mathbf{r}_k$ defined.
					
How test will be performed: The developer will create the test cases and run 
them automatically using the Unity Test Framework.

\end{enumerate}

\begin{longtable}{c c c c c c c}
\caption{Initial Flocking Parameters} \label{TblFlockParameters} \\
\hline
$N$ & ${\Delta t}\text{(s)}$ & $k_a$ & $k_c$ & $k_s$ & $k_o$ & $k_g$ \\
\hline
100 & 0.01 & 0.5 & 0.5 & 0.5 & 0.5 & 0.5 \\
\hline
\end{longtable}

\begin{longtable}{c|c c|c c} 
\caption{Input and Output - Obstacles} \label{TblITObstacles} \\
\hline
\multicolumn{1}{c|}{Index} & \multicolumn{2}{c|}{Input} & \multicolumn{2}{c}{Output} \\
\hline
& $\mathbf{p}_k\text{(m,m)}$ & $\mathbf{r}_k\text{(m)}$ & Valid? & Error Message \\
\hline
OTF\refstepcounter{oitnum}\theoitnum & (100, 100) & 50 & Y & No error message.\\
\hline
OTF\refstepcounter{oitnum}\theoitnum & - & - & Y & No error message.\\
\hline
OTF\refstepcounter{oitnum}\theoitnum & (-900, 100) & 50 & N & For $\mathbf{p}_k\text{(x,y)}$, x and y must be in [-500,1000].\\
\hline
OTF\refstepcounter{oitnum}\theoitnum & (100, 100) & -50 & N & $\mathbf{r}_k$ must be in [1, 500].\\
\hline
OTF\refstepcounter{oitnum}\theoitnum & - & 50 & N & Data missing for $\mathbf{p}_k$.\\
\hline
\end{longtable}

\paragraph{Input Tests for Integration Methods}

\begin{enumerate}
\item{test-input-method\\}

Control: Automatic
					
Initial State: There is no obstacle, and the flocking parameters is in 
Table~\ref{TblFlockParameters}.
					
Input: The Input column in Table~\ref{TblITMethods}
					
Output: The Output column in Table~\ref{TblITMethods}

Test Case Derivation: The software currently supports only the Explicit 
Euler (EEuler), Runge-Kutta 4 (RK4), and Semi-Implicit Euler (SIEuler) methods.
					
How test will be performed: The developer will create the test cases and run 
them automatically using the Unity Test Framework.

\end{enumerate}

\begin{longtable}{c|c|c c}
\caption{Input and Output - Methods} \label{TblITMethods} \\
\hline
\multicolumn{1}{c|}{Index} & \multicolumn{1}{c|}{Input} & \multicolumn{2}{c}{Output} \\
\hline
& $\mathbf{M}$ & Valid? & Error Message \\
\hline
MTF\refstepcounter{mitnum}\themitnum & EEuler & Y & No error message.\\
\hline
MTF\refstepcounter{mitnum}\themitnum & Euler & N & $\mathbf{M}$ must be in \{EEuler, RK4, SIEuler\}.\\
\hline
MTF\refstepcounter{mitnum}\themitnum & - & N & Data missing for$\mathbf{M}$.\\
\hline
\end{longtable}

\subsubsection{Test of Motion Logic} \label{motionTest}

This section covers R4, R5 and R6 from the \citet{SRS}. Due to the lack of 
directly comparable datasets for the software outputs, the accuracy of the 
models executed by the software will be primarily ensured through static code 
analysis and unit tests. In this context, the functional test cases for 
flocking dynamics focus on verifying the overall trends and expected behaviors 
of the agents rather than exact numerical values.

\paragraph{Test of Motion Logic}

\begin{enumerate}

\item{single-agent-motion\\} \label{singleAgentTest}

Control: Automatic and Manual
					
Initial State: There is one one agent, with initial positions at (0, 0).
					
Input: The Input column in Table~\ref{TblMotionTest0}
					
Output: The agent positions file, animation.

Test Case Derivation: For flocking with only one agent, according to DD4, 
DD5, DD6, DD7, and DD8 in the \citet{SRS}, the agent is driven solely by the 
goal seeking force. In this case, the agent's motion behavior becomes predictable.

How test will be performed: 
\begin{itemize}
\item The agent is always influenced only by the force defined as DD8 in 
the \citet{SRS}, and locating at line y = x.
\item In the animation, it can be clearly observed that the agent move 
directly to the goal point.
\end{itemize}

\begin{longtable}{c c c c c c c c c c}
\caption{Input of single-agent-motion} \label{TblMotionTest0} \\
\hline
$N$ & ${\Delta t}\text{(s)}$ & $k_a$ & $k_c$ & $k_s$ & $k_o$ & $k_g$ & $\mathbf{p}_1\text{(m,m)}$ & $\mathbf{r}_1\text{(m)}$ & $\mathbf{M}$ \\
\hline
1 & 0.01 & 0.5 & 0.5 & 0.5 & 0.5 & 0.5 & - & - & SIEuler \\
\hline
\end{longtable}

\item{two-agent-symmetric-motion\\} \label{symmetricTest}

Control: Automatic and Manual
					
Initial State: There are only two agents, with initial positions at (0.5, 1) 
and (1, 0.5), respectively.
					
Input: The Input column in Table~\ref{TblMotionTest1}
					
Output: The agent positions file, animation, the flocking center $\mathbf{p}_t$ , the flock 
cohesion $\mathbf{C}_\mathbf{t}$.

Test Case Derivation: For flocking with only two agents, according to DD4, 
DD5, DD6, DD7, and DD8 in the \citet{SRS}, when their initial positions, 
obstacles, and the goal point are all symmetric with respect to the line $y=x$, 
the forces they experience at the initial step are also symmetric about 
$y=x$. Consequently, this symmetry is preserved at every subsequent time step. 
For these two agents, a flocking center, in other words, the midpoint between 
them, necessarily located at on the symmetry axis.

How test will be performed: 
\begin{itemize}
\item For  $\mathbf{p}_t(x,y)$, $|x-y|=0$.
\item In the animation, it can be clearly observed that the two agents move 
symmetrically with respect to the line $y=x$.
\end{itemize}
In the actual implementation, minor deviations may occur due to floating-point 
arithmetic. Since this is a continuous animation, the state of an agent at 
any given moment affects its subsequent states, so the longer the simulation 
runs, the larger the deviation may become.

\begin{longtable}{c c c c c c c c c c}
\caption{Input of two-agent-symmetric-motion} \label{TblMotionTest1} \\
\hline
$N$ & ${\Delta t}\text{(s)}$ & $k_a$ & $k_c$ & $k_s$ & $k_o$ & $k_g$ & $\mathbf{p}_1\text{(m,m)}$ & $\mathbf{r}_1\text{(m)}$ & $\mathbf{M}$ \\
\hline
2 & 0.01 & 0.5 & 0.5 & 0.5 & 0.5 & 0.5 & (200, 200) & 50 & SIEuler \\
\hline
\end{longtable}

\item{single-weight-zero\\} \label{zeroWeightTest}

Control: Automatic and Manual
					
Initial State: There are only two agents, with initial positions at (0.5, 1) 
and (1, 0.5), respectively.
					
Input: The Input column in Table~\ref{TblMotionTest2}
					
Output: The agent positions file, animation, the flocking center $\mathbf{p}_t$ , the flock 
cohesion $\mathbf{C}_\mathbf{t}$.

Test Case Derivation: Similar to \ref{symmetricTest}, this test also ensures 
that the two agents remain symmetric with respect to the line $y=x$ at all 
times. However, due to the absence of the separation force within the 
flocking model, even if the agents start very close to each other, they lack 
the repulsive force between them. As a result, the flocking cohesion in this 
test is expected to be smaller than in \ref{symmetricTest}.

How test will be performed: 
\begin{itemize}
\item For the majority of the simulation time, the $\mathbf{C}_\mathbf{t}$ 
value in this test is expected to be smaller than that of \ref{symmetricTest}.
\item The flocking center is required to lie on the line $y=x$.
\item In the animation, it can be clearly observed that the two agents move 
symmetrically with respect to the line $y=x$. And compared to \ref{symmetricTest}, 
the two agents are positioned closer to each other.
\end{itemize}
Similar to \ref{symmetricTest}, this test may also exhibit deviations due to 
floating-point computations.

\begin{longtable}{c c c c c c c c c c}
\caption{Input of single-weight-zero} \label{TblMotionTest2} \\
\hline
$N$ & ${\Delta t}\text{(s)}$ & $k_a$ & $k_c$ & $k_s$ & $k_o$ & $k_g$ & $\mathbf{p}_1\text{(m,m)}$ & $\mathbf{r}_1\text{(m)}$ & $\mathbf{M}$ \\
\hline
2 & 0.01 & 0.5 & 0.5 & 0 & 0.5 & 0.5 & (200, 200) & 50 & SIEuler \\
\hline
\end{longtable}

\end{enumerate}

\subsubsection{Boundary Testing of Variables} \label{boundaryTest}

This section covers R5 and R7 from the \citet{SRS}. Since the boundaries 
can be computed and compared, this section focuses on numerical values 
rather than overall trends.

\paragraph{Boundary Testing of Velocity}

\begin{enumerate}

\item{maximum-velocity-verification\\} \label{maxVTest}

Control: Automatic
					
Initial State: None.
					
Input: The Input column in Table~\ref{TblBoundTest1}
					
Output: The agent positions file, agent speed $\mathbf{v}_{i,t}$.

Test Case Derivation: To prevent the flocking behavior from diverging, a 
maximum velocity constraint must be enforced for each agent.

How test will be performed: 
\begin{itemize}
\item $\forall t \ge 0,\; \forall i \in \{1,\dots,N\},\; \|\mathbf{v}_{i,t}\| \le v_{max}$
\end{itemize}
$v_{max}$ is defined as 20.

\begin{longtable}{c c c c c c c c c c}
\caption{Input of maximum-velocity-verification} \label{TblBoundTest1} \\
\hline
$N$ & ${\Delta t}\text{(s)}$ & $k_a$ & $k_c$ & $k_s$ & $k_o$ & $k_g$ & $\mathbf{p}_1\text{(m,m)}$ & $\mathbf{r}_1\text{(m)}$ & $\mathbf{M}$ \\
\hline
100 & 0.01 & 0.5 & 0.5 & 0.5 & 0.5 & 0.5 & (200, 200) & 50 & EEuler \\
100 & 0.01 & 0.5 & 0.5 & 0.5 & 0.5 & 0.5 & (200, 200) & 50 & RK4 \\
100 & 0.01 & 0.5 & 0.5 & 0.5 & 0.5 & 0.5 & (200, 200) & 50 & SIEuler \\
\hline
\end{longtable}
\end{enumerate}

\subsubsection{Testing of Integration Methods} \label{methodTest}

This section covers R3, R5 and R7 from the \citet{SRS}. It focuses on 
verifying the overall trends presented in the line charts.

\paragraph{Integration Method Verification}

\begin{enumerate}

\item{compare-different-timestep\\} \label{timestepVTest}

Control: Automatic
					
Initial State: None.
					
Input: The Input column in Table~\ref{TblMethodTest1}
					
Output: The agent positions file.

Test Case Derivation: Since numerical integration methods discretize 
continuous dynamics for computation, theoretically, the smaller the time step, 
the smaller the differences among the results produced by different numerical 
integration methods.

How test will be performed: 
\begin{itemize}
\item Throughout the entire simulation, the difference in agent position among 
the different numerical integration methods is larger than the corresponding 
value in \ref{maxVTest}.
\end{itemize}

\begin{longtable}{c c c c c c c c c c}
\caption{Input of compare-different-timestep} \label{TblMethodTest1} \\
\hline
$N$ & ${\Delta t}\text{(s)}$ & $k_a$ & $k_c$ & $k_s$ & $k_o$ & $k_g$ & $\mathbf{p}_1\text{(m,m)}$ & $\mathbf{r}_1\text{(m)}$ & $\mathbf{M}$ \\
\hline
100 & 0.1 & 0.5 & 0.5 & 0.5 & 0.5 & 0.5 & (200, 200) & 50 & EEuler \\
100 & 0.1 & 0.5 & 0.5 & 0.5 & 0.5 & 0.5 & (200, 200) & 50 & RK4 \\
100 & 0.1 & 0.5 & 0.5 & 0.5 & 0.5 & 0.5 & (200, 200) & 50 & SIEuler \\
\hline
\end{longtable}
\end{enumerate}

\subsection{Tests for Nonfunctional Requirements} \label{test_nonfunc}

The nonfunctional requirements can be found in Section 5.2 of the \citet{SRS}. 
All four nonfunctional requirements will be addressed in the following sections.

\subsubsection{Correctness} \label{correctTest}

The correctness of the software implementation can be verified through the 
functional test cases in \ref{test_func} and the unit tests.

\subsubsection{Verifiability} \label{verifyTest}

The verifiability requirement is satisfied by demonstrating that all SRS 
requirements are linked to specific test cases in the traceability matrix, 
ensuring full coverage of the verification and validation activities. The 
specific traceability mappings can be found in Section~\ref{secTrace}.

\subsubsection{Usability} \label{usabilityTest}

Usability focuses on whether the graphical user interface of the software is 
clear, and easy to use. So this aspect will be evaluated based on user feedback.
		
\paragraph{Usability Test}

\begin{enumerate}

\item{test-usability\\}

Type: Manual with potential users.
					
Initial State: The software is set up and ready for testing.
					
Input/Condition: None.
					
Output/Result: Survey about the user experience with software.
					
How test will be performed: After using the software, users will be asked to 
complete a survey(~\ref{usablitySurvey}) based on their experience to 
evaluate the usability of the software.

\end{enumerate}

\subsubsection{Realism} \label{realismTest}

Realism shows if this software generate a realistic flocking simulation 
animation. Realism is something that is difficult to quantify with data, so 
it needs users' feedback.
		
\paragraph{Realism Test} \label{realismTestCase}

\begin{enumerate}

\item{test-realism\\}

Type: Manual with classmates and professor, consisting of 6-8 volunteers from 
the CAS 741 class.
					
Initial State: The software is set up and ready for testing, and a set of 
relatively appropriate input parameters has already been identified.
					
Input/Condition: None.
					
Output/Result: Survey about the user experience with software.
					
How test will be performed: After showing the using demo of software, users will 
be asked to complete a survey(~\ref{realismSurvey}) based on their experience to 
evaluate the realism of the simulated flocking animation.

\end{enumerate}

\subsubsection{Maintainability} \label{maintainTest}

The correctness of the software implementation can be verified through the 
functional test cases in \ref{test_func} and the unit tests. Requirements 
related to realism will be validated using \ref{realismTestCase} described 
below.
		
\paragraph{Maintainability Test}

\begin{enumerate}

\item{test-maintainability\\} 

Type: Manual.
					
Initial State: The software has completed the implementation of its
core functionalities, and the total development time has been recorded
as $T_{dev}$.
					
Input/Condition: Adding support for a new feature, such as supporting
a new numerical integration method, Runge-Kutta 3.
					
Output/Result: Implementing the corresponding feature and record
the time required as $T_{add}$.
					
How test will be performed: Compare the original development time $T_{dev}$ with 
the time required to implement the new feature $T_{add}$ to verify whether it 
satisfies the requirement of NFR4.

\end{enumerate}

\subsection{Traceability Between Test Cases and Requirements} \label{secTrace}

The traceability between test cases and requirements is shown in Table~\ref{tblTrace}.

\begin{table}[h!]
\caption{Traceability Between Test Cases And Requirements} \label{tblTrace} 
\centering
\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|c|c|}
\hline
	& R1 & R2 & R3 & R4 & R5 & R6 & R7 & NFR1 & NFR2 & NFR3 & NFR4 & NFR5 \\
\hline
\ref{inputTest}                &X&X& & & & & & & & & & \\ \hline
\ref{motionTest}               & & & &X&X&X& &X& & & & \\ \hline
\ref{boundaryTest}             & & & & &X& &X&X& & & & \\ \hline
\ref{methodTest}               & & &X& &X& &X& & & & & \\ \hline
\ref{correctTest}              & & & & & & & &X& & & & \\ \hline
\ref{verifyTest}               & & & & & & & & &X& & & \\ \hline
\ref{usabilityTest}            & & & & & & & & & &X& & \\ \hline
\ref{realismTest}              & & & & & & & & & & &X& \\ \hline
\ref{maintainTest}             & & & & & & & & & & & &X\\ \hline
\end{tabular}
\end{table}

\section{Unit Test Description} \label{sec_unittest}

Unit tests are used to verify the modules defined in the 
\href{https://mei0725.github.io/FlockingSimulator/Design/SoftArchitecture/MG.pdf}{MG} and 
\href{https://mei0725.github.io/FlockingSimulator/Design/SoftArchitecture/MIS.pdf}{MIS}. 
For most modules, a special test file was created. Each module is tested for 
expected, boundary, and exceptional cases. The tests are automatically 
triggered by GitHub Actions whenever code in the \textbackslash src directory 
is modified, helping ensure that existing functionality is not broken during 
development.

\subsection{Unit Testing Scope}

Unit tests are performed on all modules developed for \progname{}, except:
\begin{enumerate}
  \item Hardware-Hiding Module(M1): Its functionality depends on external 
  hardware and runtime environment interactions, which are not easy to create 
  unit test.
  \item Flocking Parameter Module(M8): It is a simple record type ,and its 
  functionality is already exercised and verified through other tests, so no 
  separate unit test was created for it.
  \item Animation Status Module(M9): It is a simple record type ,and its 
  functionality is already exercised and verified through other tests, so no 
  separate unit test was created for it.
  \item Flocking Status Module(M10): It is a simple record type ,and its 
  functionality is already exercised and verified through other tests, so no 
  separate unit test was created for it.
\end{enumerate}

\subsubsection{Main Control Module [MG: M2]} \label{UTMain}

This test verifies whether the prompt color displayed on the main UI is correct 
and whether the associated methods are triggered properly.
See \href{https://github.com/Mei0725/FlockingSimulator/blob/main/src/Assets/Tests/MainControllerTests.cs}{MainControllerTests}
\begin{enumerate}
  \item InitClicked\_Success\_Should\_Set\_Green\_Text
  \item InitClicked\_Error\_Should\_Set\_Red\_Text
  \item CalculateClicked\_Success
  \item CalculateClicked\_Error
  \item PlayAnimaClicked\_Should\_Call\_Simulator
  \item PlayAnimaClicked\_Error
  \item DrawClicked\_Should\_Call\_DrawChart
  \item DrawClicked\_Error
\end{enumerate}

\subsubsection{Input Validation Module [MG: M3]} \label{UTInputValid}

This test verifies whether input parameters are validated correctly and whether 
the appropriate exceptions are thrown.
See \href{https://github.com/Mei0725/FlockingSimulator/blob/main/src/Assets/Tests/IO/InputValidationTests.cs}{InputValidationTests}
\begin{enumerate}
  \item KVerify\_Valid\_Should\_Return\_value
  \item KVerify\_Empty\_Should\_Throw\_MissingK
  \item KVerify\_OutOfRange\_Should\_Throw\_ErrorK
  \item NVerify\_Valid
  \item NVerify\_Invalid\_Should\_Throw\_ErrorN
  \item TVerify\_Valid
  \item TVerify\_Invalid\_Should\_Throw\_ErrorT
  \item ObsVerify\_Valid\_Input
  \item ObsVerify\_MissingRadius\_Should\_Throw
  \item ObsVerify\_InvalidPosition\_Should\_Throw
  \item MethodVerify\_Valid
  \item MethodVerify\_Empty\_Should\_Throw
  \item MethodVerify\_Invalid\_Should\_Throw
  \item PathVerify\_Valid
  \item PathVerify\_Empty\_Should\_Throw
\end{enumerate}

\subsubsection{Force Module [MG: M4]} \label{UTForce}

This test verifies whether the internal flocking force calculations are 
correct in very simple single-agent or two-agent scenarios.
See \href{https://github.com/Mei0725/FlockingSimulator/blob/main/src/Assets/Tests/FlockingCalculator/ForceTests.cs}{ForceTests}
\begin{enumerate}
  \item CalAlignForce\_Should\_Point\_To\_Other\_Velocity
  \item CalAlignForce\_Single\_Should\_Be\_Zero
  \item CalCohesionForce\_Should\_Point\_To\_Center
  \item CalCohesionForce\_Single\_Should\_Be\_Zero
  \item CalSeparationForce\_Should\_Repel
  \item CalSeparationForce\_Single\_Should\_Be\_Zero
  \item CalObsAvoidForce\_Should\_Repel\_From\_Obstacle
  \item CalObsAvoidForce\_NoObstacle\_Should\_Be\_Zero
  \item CalGoalSeekingForce\_Should\_Point\_To\_Goal
  \item CalGoalSeekingForce\_WithVelocity\_Should\_Adjust
  \item CalForce\_Should\_Return\_Combined\_Force
\end{enumerate}

\subsubsection{ODEs Solver Module [MG: M5]} \label{UTSolver}

This test verifies whether the ODE solver output format is correct and whether 
certain special inputs are handled without errors.
See \href{https://github.com/Mei0725/FlockingSimulator/blob/main/src/Assets/Tests/FlockingCalculator/ODESolverTests.cs}{ODESolverTests}
\begin{enumerate}
  \item EEulerMethod\_Should\_Return\_Correct\_Size
  \item SIEulerMethod\_Should\_Update\_Position\_And\_Velocity
  \item RK4Method\_Should\_Return\_Valid\_Output
  \item EEuler\_Should\_Not\_Throw
\end{enumerate}

\subsubsection{Flocking Metrics Module [MG: M6]} \label{UTFlockParam}

This test verifies whether flocking metrics are calculated correctly in very 
simple single-agent or two-agent scenarios.
See \href{https://github.com/Mei0725/FlockingSimulator/blob/main/src/Assets/Tests/FlockingCalculator/FlockingMetricsTests.cs}{FlockingMetricsTests}
\begin{enumerate}
  \item CalMeanSpeed\_Should\_Return\_Correct\_Average
  \item CalAlignMetric\_SameDirection\_Should\_Be\_1
  \item CalAlignMetric\_OppositeDirection\_Should\_Be\_0
  \item CalCenter\_Should\_Return\_Correct\_Center
  \item CalCohesion\_Should\_Calculate\_Average\_Distance
  \item CalCohesion\_WithCenter\_Should\_Match
  \item CalMeanSpeed\_SingleElement
\end{enumerate}

\subsubsection{Dynamics Module [MG: M7]} \label{UTDyna}

This test verifies whether the output format is correct and whether some 
exceptional inputs can be handled properly.
See \href{https://github.com/Mei0725/FlockingSimulator/blob/main/src/Assets/Tests/FlockingCalculator/DynamicsTests.cs}{DynamicsTests}
\begin{enumerate}
  \item FlockSimulation\_Should\_Return\_Result
  \item FlockSimulation\_Should\_Initialize\_Animation
  \item FlockSimulation\_Should\_Generate\_Metrics
  \item FlockSimulation\_Should\_Run\_EEuler
  \item FlockSimulation\_Should\_Run\_RK4
  \item FlockSimulation\_Should\_Run\_ISEULER
  \item FlockSimulation\_Should\_Handle\_Invalid\_Method
  \item FlockSimulation\_Should\_Append\_Positions
\end{enumerate}

\subsubsection{Input Reader Module [MG: M11]} \label{UTReader}

This test verifies whether valid inputs can be correctly read from the UI.
See \href{https://github.com/Mei0725/FlockingSimulator/blob/main/src/Assets/Tests/IO/InputReaderTests.cs}{InputReaderTests}
\begin{enumerate}
  \item GetUserInput\_Should\_Return\_Valid\_Object
  \item GetSimulateParam\_InvalidPath\_Should\_Throw
  \item GetMethod\_Should\_Map\_Correctly
  \item GetAnimaStatus\_Should\_Read\_Multiple\_Files
  \item GetFlockStatus\_Should\_Read\_Files
  \item GetAnimaStatus\_Empty\_Should\_Return\_Empty\_List
\end{enumerate}

\subsubsection{File I/O Module [MG: M12]} \label{UTIO}

This test verifies whether files can be written and read successfully, as well 
as whether missing-file exceptions are handled properly.
See \href{https://github.com/Mei0725/FlockingSimulator/blob/main/src/Assets/Tests/IO/FilesIOTests.cs}{FilesIOTests}
\begin{enumerate}
  \item Write\_Should\_Create\_File
  \item Write\_Should\_Contain\_Correct\_JSON
  \item Read\_Should\_Return\_Data
  \item Read\_Should\_Throw\_When\_File\_Not\_Found
\end{enumerate}

\subsubsection{Animation Simulator Module [MG: M13]} \label{UTAnime}

This test verifies whether the animation runs correctly, and whether the 
number of agents and obstacle rendering are correct.
See \href{https://github.com/Mei0725/FlockingSimulator/blob/main/src/Assets/Tests/Visualization/AnimationSimulatorTests.cs}{AnimationSimulatorTests}
\begin{enumerate}
  \item PlaySimulation\_SingleAnimation\_StartsCorrectly
  \item PlaySimulation\_WhenAlreadyPlaying\_ShouldNotStart
  \item PlaySimulation\_MultipleAnimations\_EnableLabels
  \item Simulation\_EmptyAgents\_ShouldExitEarly
  \item DrawObstacles\_ShouldCreateGameObjects
\end{enumerate}

\subsubsection{Chart Drawer Module [MG: M14]} \label{UTChart}

This test verifies whether charts are displayed correctly, whether the number 
of plotted lines is correct, and whether reading multiple input files works 
properly.
See \href{https://github.com/Mei0725/FlockingSimulator/blob/main/src/Assets/Tests/Visualization/ChartDrawerTests.cs}{ChartDrawerTests}
\begin{enumerate}
  \item Start\_Should\_Initialize\_Charts
  \item DrawChart\_Should\_Not\_Throw
  \item DrawChart\_Should\_Add\_Series
  \item DrawChart\_MultipleInputs\_Should\_Work
\end{enumerate}

\subsection{Tests for Functional Requirements}

This module introduces the test cases for Functional Requirements implemented 
using the Unity Test Framework.

\subsubsection{Input Test[\ref{inputTest}]} \label{FTInput}

This test verifies various valid and invalid input parameters and checks 
whether the correct exceptions are thrown.
See \href{https://github.com/Mei0725/FlockingSimulator/blob/main/src/Assets/Tests/IO/InputReaderTests.cs}{InputReaderTests}
\begin{enumerate}
  \item Functional\_Test\_Exception
  \item Functional\_Test\_Obs
\end{enumerate}

\subsubsection{Flocking Test[\ref{motionTest}, \ref{boundaryTest}, \ref{methodTest}]} \label{FTFlocking}

This test verifies whether multiple flocking simulation scenarios with 
predictable outputs behave as expected.
See \href{https://github.com/Mei0725/FlockingSimulator/blob/main/src/Assets/Tests/FunctionalTest/FunctionalTest.cs}{FunctionalTest}
\begin{enumerate}
  \item Single\_Agent\_Verify
  \item Symmetry\_And\_NoSepa\_Verify
  \item MaxVelo\_And\_DiffODE\_Verify
\end{enumerate}

\subsection{Tests for Nonfunctional Requirements}

Unit testing the non-functional requirements is beyond the scope. Tests
related to non-functional requirements of system are introduced in 
section \ref{test_nonfunc}.

\subsection{Traceability Between Test Cases and Modules}

\begin{table}[h!]
\caption{Traceability Between Test Cases and Modules} \label{tblTraceToModule} 
\centering
\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|}
\hline
	& M2 & M3 & M4 & M5 & M6 & M7 & M11 & M12 & M13 & M14 \\
\hline
Test \ref{UTMain}           &X& & & & & & & & &\\ \hline
Test \ref{UTInputValid}     & &X& & & & & & & &\\ \hline
Test \ref{UTForce}          & & &X& & & & & & &\\ \hline
Test \ref{UTSolver}         & & & &X& & & & & &\\ \hline
Test \ref{UTFlockParam}     & & & & &X& & & & &\\ \hline
Test \ref{UTDyna}           & & & & & &X& & & &\\ \hline
Test \ref{UTReader}         & & & & & & &X& & &\\ \hline
Test \ref{UTIO}             & & & & & & & &X& &\\ \hline
Test \ref{UTAnime}          & & & & & & & & &X&\\ \hline
Test \ref{UTChart}          & & & & & & & & & &X\\ \hline
Test \ref{FTInput}          & &X& & & & & & & &\\ \hline
Test \ref{FTFlocking}       & & &X&X&X&X& & & &\\ \hline
\end{tabular}
\end{table}
				
\bibliographystyle{plainnat}

\bibliography{../../refs/References}

\newpage

\section{Appendix}

This is where you can place additional information.

% \subsection{Symbolic Parameters}

% The definition of the test cases will call for SYMBOLIC\_CONSTANTS.
% Their values are defined in this section for easy maintenance.

\subsection{Simulation Realism Survey Questions} \label{realismSurvey}

\begin{enumerate}
\item From one to five and five being the most satisfied, how realistic do you 
find the final animation?
\item Based on your experience, please rank the realism of the animations 
generated by the different parameter sets.
\end{enumerate}

\subsection{Usability Survey Questions} \label{usablitySurvey}

\begin{enumerate}
\item From one to five and five being the most satisfied, how would you rate 
your overall experience of this software?
\item From one to five and five being the most satisfied, how clear and easy 
to understand do you find the variable input UI?
\item From one to five and five being the most satisfied, how would you rate 
the speed and responsiveness of this software?
\item From one to five and five being the most satisfied, how clear and easy 
to understand do you find the output line charts?
\item Do you think the software includes all the features you want? If not, 
please specify which features are missing.
\end{enumerate}

% \newpage{}
% \section*{Appendix --- Reflection}

% \wss{This section is not required for CAS 741}

% The information in this section will be used to evaluate the team members on the
% graduate attribute of Lifelong Learning.

% \input{../Reflection.text}

% \begin{enumerate}
%   \item What went well while writing this deliverable? 
%   \item What pain points did you experience during this deliverable, and how
%     did you resolve them?
%   \item What knowledge and skills will the team collectively need to acquire to
%   successfully complete the verification and validation of your project?
%   Examples of possible knowledge and skills include dynamic testing knowledge,
%   static testing knowledge, specific tool usage, Valgrind etc.  You should look to
%   identify at least one item for each team member.
%   \item For each of the knowledge areas and skills identified in the previous
%   question, what are at least two approaches to acquiring the knowledge or
%   mastering the skill?  Of the identified approaches, which will each team
%   member pursue, and why did they make this choice?
% \end{enumerate}

\end{document}